### 2015-02-08 docs/report/serialization_transference.tex

These were the results:
\img{Results with 100000 elements}{../../spikes/1.2/transferrableVsCloning}{}{fig:transferrable-vs-cloning}

@@

These were the results:
\img{Results with 100000 elements}{../../spikes/1.2/longerTransferrableVsCloning}{fig:long-transferrable-vs-cloning}

>>>>

The results for it are displayed in Figure~\ref{fig:transferrable-vs-cloning}.
\img{Results with 100000 elements}{../../spikes/1.2/transferrableVsCloning}{fig:transferrable-vs-cloning}

@@

The results for it are displayed in Figure~\ref{fig:long-transferrable-vs-cloning}.
\img{Results with 100000 elements}{../../spikes/1.2/longerTransferrableVsCloning}{fig:long-transferrable-vs-cloning}
